Calendar-based graphics for visualizing people's daily schedules

### 2017-08-01 main.Rmd
updated year diagram
added one more sentence to discussion

We develop a method for organizing and visualizing temporal data, collected on sub-daily interval, into a calendar layout. The purpose of the calendar-based visualization is to provide insights into people's daily schedules relative to events such as work days, weekends, holidays, and special events. This work was originally motivated by studying foot traffic in the city of Melbourne [@ped]. There have been 43 sensors installed that count pedestrians every hour across the downtown area (Figure \ref{fig:ped-map}). The dataset can shed light into understanding people's daily rhythms, to assist the city administration and local businesses with event planning and operational management. A routine examination of the data would be constructing a conventional time series plot to catch a glimpse of temporal patterns. The facetted plots in Figure \ref{fig:time-series-plot}, give an overall picture of the foot traffic at 3 different sensors over 2016. Further facetting by day of the week (Figure \ref{fig:facet-time}) provides a better glimpse at the daily and sub-daily, like commuter, patterns. The sensor data, like many temporal datasets on human behaviors, lends itself to a number of exploratory data visualization challenges:

@@

and the conventional ways to display time series and constructing facetted displays don't completely address these challenges.

@@

```{r year-diagram, out.width = "360pt", out.height = "250pt", fig.cap = "(ref:year-diagram-cap)"}
include_graphics("figure/year.pdf")
```

@@

This sort of layout may be useful for studying consumer trends, or human behavior, like the pedestrian patterns. It may not work so well for physical patterns like temperature, which are not typically affected by human activity.

>>>>

We develop a method for organizing and visualizing temporal data, collected on sub-daily interval, into a calendar layout. The purpose of the calendar-based visualization is to provide insights into people's daily schedules relative to events such as work days, weekends, holidays, and special events. This work was originally motivated by studying foot traffic in the city of Melbourne [@ped]. There have been 43 sensors installed that count pedestrians every hour across the downtown area (Figure \ref{fig:ped-map}). The dataset can shed light into understanding people's daily rhythms, to assist the city administration and local businesses with event planning and operational management. A routine examination of the data would be constructing a conventional time series plot to catch a glimpse of temporal patterns. The faceted plots in Figure \ref{fig:time-series-plot}, give an overall picture of the foot traffic at 3 different sensors over 2016. Further faceting by day of the week (Figure \ref{fig:facet-time}) provides a better glimpse at the daily and sub-daily, like commuter, patterns. The sensor data, like many temporal datasets on human behaviors, lends itself to a number of exploratory data visualization challenges:

@@

The conventional ways to display time series and constructing faceted displays are insufficient to address these challenges.

@@

```{r year-diagram, out.width = "360pt", out.height = "250pt", fig.cap = "(ref:year-diagram-cap)"}
include_graphics("figure/year-diagram.pdf")
```

@@

This sort of layout may be useful for studying consumer trends, or human behavior, like the pedestrian patterns. It may not work so well for physical patterns like temperature, which are not typically affected by human activity. Additionally, it is perceptually difficult to discover an overall trend of less significance, since there is the lack of a common baseline due to the rows and columns of a display matrix.

### 2017-08-01 main.tex
updated pdf file
updated year diagram
added one more sentence to discussion

We develop a method for organizing and visualizing temporal data,
collected on sub-daily interval, into a calendar layout. The purpose of
the calendar-based visualization is to provide insights into people's
daily schedules relative to events such as work days, weekends,
holidays, and special events. This work was originally motivated by
studying foot traffic in the city of Melbourne \citep{ped}. There have
been 43 sensors installed that count pedestrians every hour across the
downtown area (Figure \ref{fig:ped-map}). The dataset can shed light
into understanding people's daily rhythms, to assist the city
administration and local businesses with event planning and operational
management. A routine examination of the data would be constructing a
conventional time series plot to catch a glimpse of temporal patterns.
The facetted plots in Figure \ref{fig:time-series-plot}, give an overall
picture of the foot traffic at 3 different sensors over 2016. Further
facetting by day of the week (Figure \ref{fig:facet-time}) provides a
better glimpse at the daily and sub-daily, like commuter, patterns. The
sensor data, like many temporal datasets on human behaviors, lends
itself to a number of exploratory data visualization challenges:

@@

{\centering \includegraphics[width=360pt,height=250pt]{figure/year}

>>>>

We develop a method for organizing and visualizing temporal data,
collected on sub-daily interval, into a calendar layout. The purpose of
the calendar-based visualization is to provide insights into people's
daily schedules relative to events such as work days, weekends,
holidays, and special events. This work was originally motivated by
studying foot traffic in the city of Melbourne \citep{ped}. There have
been 43 sensors installed that count pedestrians every hour across the
downtown area (Figure \ref{fig:ped-map}). The dataset can shed light
into understanding people's daily rhythms, to assist the city
administration and local businesses with event planning and operational
management. A routine examination of the data would be constructing a
conventional time series plot to catch a glimpse of temporal patterns.
The faceted plots in Figure \ref{fig:time-series-plot}, give an overall
picture of the foot traffic at 3 different sensors over 2016. Further
faceting by day of the week (Figure \ref{fig:facet-time}) provides a
better glimpse at the daily and sub-daily, like commuter, patterns. The
sensor data, like many temporal datasets on human behaviors, lends
itself to a number of exploratory data visualization challenges:

@@

{\centering \includegraphics[width=360pt,height=250pt]{figure/year-diagram}
